A survey of HTTP caching options on the open Web

### 2015-01-13 sanity/paper1.tex
qqplot fig
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@974 43ef1190-90fd-4dd7-a769-d0121f02b80e

In both the cases of standard-compliant freshness time and for the
other promising features, the test reports \pvalue = 0.0001. We can
conclude that it is highly likely that some servers are better at
exposing cache headers than others. Unfortunately, since most
\httph{Server} headers only report generic values, little can be
learnt about these implementations. We note, however, that DBPedia
exposes standards-compliant freshness time of 604800 seconds (i.e. 1
week) for both LOD and SPARQL endpoints. \todo{do this specifically
  for SPARQLES endpoints?}

@@

For a visual inspection, we may use a quantile-quantile plot to plot
the freshness lifetimes of successful responses versus requests that
failed for some reason. If the distribution of both variables are the
same, these points will draw a straight line. In Figure\todo{include
  qqplot}, we see successful responses vs. the most common parse
error, and it is clear that these are so different that no further
formal analysis is necessary, we must filter unsuccessful requests in
the following analysis.

>>>>

In both the cases of standard-compliant freshness time and for the
other promising features, the test reports \pvalue = 0.0001. We can
conclude that it is highly likely that some servers are better at
exposing cache headers than others. Unfortunately, since most
\httph{Server} headers only report generic values, little can be
learnt about these implementations. We note, however, that DBPedia
exposes standards-compliant freshness time of 604800 seconds (i.e. 1
week) for both LOD and SPARQL endpoints.

@@

For a visual inspection, we may use a quantile-quantile plot to plot
the freshness lifetimes of successful responses versus requests that
failed for some reason. If the distribution of both variables are the
same, these points will lie on a straight line. In
Figure~\ref{fig:errorsqq}, we see successful responses vs. the most
common parse error, and it is clear that these are so different that
no further formal analysis is necessary, we must filter unsuccessful
requests in the following analysis.

\begin{figure}[ht!]
  \centerline{%
    \includegraphics[width=.5\textwidth]{errorsqq.pdf}}
  \caption{A quantile-quantile plot of freshness lifetimes for
    standard compliant headers with and without errors.}
  \label{fig:errorsqq}
\end{figure}
